### 2021-02-26 msc-thesis.tex
added textual descriptions

% TITLE:
\pagenumbering{roman}
\begin{titlepage}
     \vspace*{1cm}
     \begin{center}
          \vspace*{3cm}
          \textbf
          {
               \Large Universität Heidelberg\\
               \smallskip
               \Large Institute for Computer Science\\
               \smallskip
               \Large Working group database systems\\
               \smallskip
          }

@@

          \textbf{\large Bachelor thesis}

@@

     \vfill
     {
          \large
          \begin{tabular}[l]{ll}
               Name:                 & Jonas Gann              \\
               Matriculation number: & 3367576                 \\
               Supervisor:           & Prof. Dr. Michael Gertz \\
               Date of submission:   & \today
          \end{tabular}
     }

@@

\vspace*{100pt}
\noindent
I assure that I have written this bachelor thesis on my own and only used the specified sources and resources and that I followed the principles and recommendations "Responsibility in Science" of the University of Heidelberg.

@@

\chapter{Identity Management}

>>>>

% TITLE:
\pagenumbering{roman}
\begin{titlepage}
     \vspace*{1cm}
     \begin{center}
          \vspace*{3cm}
          \textbf
          {
               \Large Ruprecht-Karls-Universität Heidelberg\\
               \smallskip
               \Large Institut für Informatik\\
               \smallskip
               \Large Lehrstuhl für Datenbanksysteme\\
               \smallskip
          }

@@

          \textbf{\large Bachelor Arbeit}

@@

     \vfill
     {
          \large
          \begin{tabular}[l]{ll}
               Name:                 & Jonas Gann              \\
               Matrikelnummer: & 3367576                 \\
               Betreuer:           & Prof. Dr. Michael Gertz \\
               Datum der Abgabe:   & \today
          \end{tabular}
     }

@@

\vspace*{100pt}
\noindent
Ich versichere, dass ich diese Bachelorarbeit selbstständig verfasst und nur die angegebenen Quellen und Hilfsmittel verwendet habe.

@@

\chapter{OZG Identity Management}

### 2021-02-26 sections/10-imp_solution_integration.tex
added textual descriptions

The first step of the basic OZG use case is the creation of a user profile through the web page of the administration portal. This is not necessary any more, as user profiles are replaced by IMP identities. The user will only have to create an IMP identity.

The second step of the basic OZG use case is to login to a user profile on the web page of the administration portal. As user profiles get replaced by IMP identities, the IMP client can be used to access OZG services. The IMP client does not require authentication, as it is installed on the smart phone of the user. The user can secure his smartphone through for example biometric authentication.

The third step of the basic OZG use case is to select an administrative service which is still done through the web page of the administration portal.

The fourth step of the basic OZG use case is to fill in the application. The application is not started by the user filling in a form on the form server and submitting the result to the administration portal any more, but by requesting a relationship with the institution responsible for processing a selected application.

The web page of the administration portal displaying a selected administrative service does not contain an integration with a form server any more. Instead it displays the QR code for a relationship template provided by the institution responsible for processing the application.

For each administrative service, the institution is responsible for processing, it issues a HTTP POST request to the institution connector requesting the creation of a relationship template. The connector responds to the institution with the template IDs.

In order for the administration portal to display the correct relationship template, he requests the user to manually enter his home address. After the administration portal determined the responsible institution, he retrieves the correct template ID and displays it to the user as QR code.

If the user scans the QR code with his IMP client, the client retrieves the relationship template corresponding to the template ID of the QR code and display it. The relationship template contains a description of the selected administrative service as reason for the relationship. The template also requests the IMP identity to share several attributes, which the institution requires in order to process the application. This replaces the functionalities of the form server.

The fifth step of the basic OZG use case is to submit the application. After the user accepts the relationship template, the client sends a relationship request to the institution which created the template along with the shared attributes. The institution can accept the request and start processing the application. The IMP identity in this case has to share personal information only with the specific institution responsible for processing the application.

The sixth and seventh steps of the basic use case are no longer necessary as the application is properly delivered to the institution as result of the fifth step.

The eighth step of the basic OZG use case is the management of active applications. As each application is represented by a relationship between an institution and an IMP identity, the application can be managed by requesting a termination of the relationship and sharing the status of the relationship as part of an attribute of the institution. Termination of the relationship after approval of both parties, also prohibits the institution from further usage of personal information of the IMP identity.

The ninth step of the basic OZG use case is the communication between user profile and institutions responsible for active applications. As an active relationship is represented by a relationship, the two parties can directly communicate through the relationship.

>>>>

This section describes integration possibilities on the solution layer.
Although the eventual goal of an IMP integration is to replace user profiles, in this case, IMP identity and user profiles will be used together to solve issues described in chapter 3 without disrupting the operation of the existing system architecture. The advanced integration in chapter 5 will present a more invasive solution.

The presented solution enables users to access OZG services by connecting user profiles to existing IMP identities. Operations performed on the IMP identity will then be synchronized with the connected user profile.

\subsection{Create User Profile}
One way to connect user profile and IMP identity is by creating a new user profile based on an existing IMP identity. The web page of the administration portal responsible for guiding the user through the user profile creation steps can present an additional option of creating a user profile called "Login using IMP Identity". A relationship template can be displayed in form of a QR code with the following content:

\begin{itemize}
    \item Title: Create OZG User Profile
    \item Attributes: Name, Surname, ... 
    \item Shared Attributes: Administration Portal of the member state ...
    \item Reason: Create an OZG user profile and connect your IMP identity.
\end{itemize}

The user can scan the QR code using his IMP client and is presented with the relationship template. As part of the template, the user is requested to share attributes which thee IMP client can automatically fill in if they already exist. The attributes requested as part of the template have to be sufficient for creating an OZG user profile.
The user is also presented with an explanation for what the purpose of the relationship is and why the specified attributes are required. If the user accepts, a relationship request can be sent to the administration portal, where the attributes can be analyzed. Depending on the result of the analysis, the relationship can be accepted and therefore established or rejected.
Once the relationship is established, the OZG system architecture can create a new user profile based on the shared attributes and store the connection of user profile and IMP identity.

\subsection{Authentication}
Communication between IMP system and administration portal can assumed to be secure: Messages originating from an IMP identity for an IMP relationship can not be accessed or modified by a third party and are authorized by the corresponding user. Therefore messages exchanged as part of the established relationship can be used to provide the IMP identity access to OZG services. Some examples for this are shown in the following sections.

\subsection{Login to User Profile}
Messages trough the established IMP relationship can be used to enable the user to access OZG services through the existing web page, by using the IMP client for authentication. After receiving a login request for a user profile on the web page of the administration portal, an authentication request containing the session ID can be sent to the IMP relationship corresponding to the user profile. The IMP client can display an appropriate notification with options for the user to accept or reject the request. The IMP client sends the result back to the administration portal which according to the response authenticates the browser session or not.

\subsection{Attribute Synchronization}
Modifications of the personal information stored in the user profile can be done by exchanging messages trough the established IMP relationship. Through the IMP client, the user can send an attribute change request regarding the relationship. The system architecture can map the relationship to the connected user profile, evaluate the request and if accepted, perform the modification of personal information. It is possible to enable the user to update attributes of his user profile trough the web page which would require the OZG system to send attribute change requests to the IMP client. For simplicity, this option is left out and the profile management web page is expected to be inaccessible for user profiles connected to IMP.

\subsection{Communication}
Messages sent to the inbox of the user profile can be forwarded to the inbox of the IMP identity. As the exchange of messages through the IMP system is secure, also security relevant information can be shared.

\subsection{Application}
To minimize the invasiveness of the integration, applications for administrative services remain to be done on the administration portal trough user profiles.

### 2021-02-26 sections/11-technological_integration.tex
added textual descriptions

\begin{itemize}
    \item Integration only with administration portal to be non invasive
    \item Only one connector for the administration portal
\end{itemize}

@@

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/1. Integration Overview.pdf}
\end{center}

System architecture of the SP and IMP system consist of multiple components. The administration portal component of the system architecture is the component which will interact with the integration system. The administration portal contains a web server and a service facade. The service facade enables the administration portal amongst other things to access the user profile component.

On the side of the IMP system, the connector will interact with the integration system.

@@

@@

The integration system consists of messaging modules, each of them solving a different integration task. The modular approach enables the integration system to be easily expandable by new features trough new modules. Assigning integration tasks to modules also improves maintenance. System administrators can update a feature by modifying and expanding the corresponding component.
Modules can be designed to be reusable by other components which reduces the development time for new features and the size of the integration system. If the modules supports it, the performance of the integration system can be dynamically scaled by adding multiple module instances.

Modules have the purpose of solving integration tasks by providing access to features presented in section 5.1 while hiding the complexity of the operation of the IMP system. Modules therefore exchange messages through three types of publish-subscribe channels. Between administration portal and modules, feature channels are used. On these channels, messages strongly related to the operation of the system architecture of the service provider are exchanged. This are for example messages for requesting services like the transmission of a mail.

@@

\begin{itemize}
    \item Web Server has messaging adapter with API for retrieving onboarding template

    \item Connector has messaging adapter with API for creating templates

    \item Onboarding Template Module exists, which manages the exchange of request and reply messages

    \item Module exchanges messages with web server adapter through request and reply channel. Only this module and the adapter of the web server use the channels.

    \item Module exchanges messages with connector adapter through request reply channel. Multiple different modules can use the channels.

    \item Config Enricher adds suitable configuration as new entry to request

    \item Configuration is stored in a database or file. An administrator maintains the configuration

    \item The configuration creates a relationship template used to create a user profile. The configuration has to define the template to require attributes necessary for creating a user profiles.

    \item Attribute names and meaning can differ between OZG user profile and IMP identity, the configuration has to use the attribute definition of the IMP system.

    \item Config Message Translator incorporates the metadata entry to the template configuration

    \item Adapter Message Translator incorporates mapping of possible future changes of adapters in for example attribute naming or attribute data types (this type of message translator can be added to every channel connected to an adapter and is therefore excluded in future visualizations)

    \item Module filters for templates of the onboarding type as the channel could contain responses with templates of different type for other modules.

\end{itemize}

@@

Eventually, the user sends a relationship request which will be processed by the "Onboarding Request Module"

@@

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Attribute Change Message Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Request Module.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Onboarding Relationship Module.pdf}
\end{center}

@@

@@

@@

@@

@@

>>>>

@@

For the existing system architecture to access the IMP system, an IMP connector is added to the portal domain. The connector communicates with an IMP client trough the IMP server located in the IMP domain.

@@

System architecture of the SP and IMP system consist of multiple components. The administration portal component of the system architecture  will interact with the integration system. The administration portal contains a web server and a service facade. The service facade enables the administration portal amongst other things to access the user profile component. On the side of the IMP system, the connector will interact with the integration system.

@@

The integration system consists of messaging modules, each of them solving a different integration task. The modular approach enables the integration system to be easily expandable by new features trough new modules. Assigning integration tasks to modules also improves maintenance. System administrators can update a feature by modifying and expanding the corresponding module.
Modules can be designed to be reusable by other components which reduces the development time for new features and the size of the integration system. If the modules supports it, the performance of the integration system can be dynamically scaled by adding more module instances.

Modules have the purpose of solving integration tasks by providing access to features presented in section 5.1 while hiding the complexity of the operation of the IMP system. They exchange messages through three types of publish-subscribe channels. Between administration portal and modules, feature channels are used. On these channels, messages strongly related to the operation of the system architecture of the service provider are exchanged. This are for example messages for requesting services like the transmission of a mail.

@@

@@

To present an onboarding relationship template to the user, the web server first has to retrieve it from the integration system. For this purpose, an "Onboarding Template Module" is added to the messaging system. Using the API of a messaging adapter provided in addition to the module, the web server can request the creation of new onboarding templates. Optionally, the web server can pass additional attributes which should be stored in the metadata section of the template. In this case, the web server will want to notify the user about the successful creation of his user profile. The web server therefore adds the users current session ID as metadata to the template.

The messaging adapter is aware of the existence of two channels: the "Onboarding Template Request" channel, where it publishes its requests and the "Onboarding Template Response" channel, where it listens for responses. In order for the adapter to correlate request and reply messages, it creates a message which besides the Template Metadata contains a request ID. This ID is expected to be included in the response message. The message ID is a unique identifier and is part of every message. The module consumes messages from the "Onboarding Template Request" channel and adds an configuration object stored at a database. This configuration contains information on how relationship templates of type onboarding are supposed to look like. It specifies the title of the template, which attributes will be requested from the user, the reason why the attributes are requested and more. If the content of relationship templates should be changed in the future, depending on the severity of the changes, either a new template module can be created or the configuration stored in the database can be edited.

Purpose of the relationship template is to eventually create a new user profile based on the attributes shared by the IMP identity. Therefore, all attributes which are required to create a user profile have to be requested by the template. As the data model of the OZG systems and IMP systems are different, message translators will have to be used to translate between them. Therefore, most modules will contain a component called "Attribute Mapping" which is responsible for translating the attribute definitions of the IMP system to attribute definitions of the OZG system and vice versa. In this model however, no message translator is required, as the configuration of the template can be defined to use the IMP data model.

A message translator combines template metadata and configuration to a configuration object, the connector understands and publishes it on the "Template Request" channel.

The messaging adapter of the connector issues the appropriate REST request to the connector and publishes the resulting template along with the request ID on the "Template Response Channel". As this channel can contain responses to requests from any amount of modules concerning different template types, the "Onboarding Template Module" filters all incoming messages which contain templates of the type "onboarding" and publishes them on the "Onboarding Template Response" channel.

The messaging adapter returns the template to the web server, which based on the session ID in the template metadata can display the template as QR code to the user.

@@

Eventually, the user scans the QR code, fills in the attributes and submits a relationship request. The request is received by the connector, forwarded to the messaging adapter and published on the "Relationship Request" channel. The message contains a relationship ID created by the IMP server to uniquely identify the request and the resulting relationship. It also contains the request content with attributes shared by the user and the template the request originated from. Messages on the "Relationship Request" channel are consumed by the "Onboarding Request Module". A message filter only lets messages trough which contain templates of type onboarding. A message translator translates attributes shared by the user from the IMP data model to the OZG data model and publishes the message on the "Onboarding Request" channel.

Based on the attributes the user shares, the OZG system has to decide if the relationship should be established or not. As this process heavily depends on the use case of the relationship and on the service provider, the messaging system expects the SP to add a module called "Onboarding Request Processing Module" which consumes the request and responds with either approve or reject on the "Onboarding Response" channel. To correlate the response to the request, the message also has to contain the relationship ID. The "Onboarding Request Module" forwards the response to the "Relationship Response" channel, where the connector will further interact with the IMP system to either establish or cancel the relationship. In between a message translator can, if required, translate the format of the response attribute so that the connector understands it.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/8. Onboarding Relationship Module.pdf}
\end{center}

If the user did not retract his relationship request before the OZG system accepted it, the relationship is established and the connector receives a corresponding notification which the messaging adapter publishes on the "Relationship Established" channel. The message contains the ID of the established relationship along with all attributes shared by the user. The "Onboarding Relationship" module consumes messages from the channel and is responsible for maintaining the state of onboarding relationships. In this case, the module only processes the establishing of relationships, it could however be expanded to also process terminations of relationships.

The module processes an established relationship by initiating the creation of a new user profile. First, a message filter lets trough only messages of the onboarding type. Afterwards, each message is stored in a "Relationship Storage" database and published on the "Create User Profile Request" channel. However, before publishing the message, attributes are again mapped form the IMP data model to the OZG data model.

To create a user profile, a messaging adapter attached to the service facade of the administration portal consumes messages from the "Create User Profile Request" channel and issues the corresponding requests to the service facade for creating a new user profile based on the attributes stored in the relationship content. After successful creation of the user profile, the messaging adapter publishes a response message on the "Create User Profile Response" channel which contains the relationship ID and the newly created Profile ID.

As responses to requests from other modules might be published on this channel, the "Onboarding Relationship" module filters all messages which do not contain a relationship ID stored in the "Relationship Storage". The rest of the messages is stored in a "Profile ID / Relationship ID Mapping" database.

This database is used trough intermodule communication to map profile IDs to relationship IDs and vice versa. Modules can publish messages on the "Identity Mapping Request" channel either containing a relationship ID or profile ID attribute and receive the message containing both profile ID and relationship ID on the "Identity Mapping Response" channel. Using messaging for this form of database access enables modules to stay unaware of the complexities of the underlying data storage mechanisms. An alternative would be for modules to use the database as a shared database.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/9. Attribute Change Message Module.pdf}
\end{center}

For the messaging system to process messages being exchanged as part of relationships, message modules can be added. Their purpose is to map messages of certain types on the "Message Inbound" channel to individual message type channels so that modules can process them. They also map messages of the individual message type channels to the "Message Outbound" channel to so that the connector can submit them.

In this case, an "Attribute Change Message Module" is included, which processes messages related to the attribute change process of onboarding relationships. The connector receives a message corresponding to a relationship ID which the messaging adapter publishes on the "Message Inbound" channel. The message contains the ID of the relationship it was exchanged trough, an identification of the message type and the content of the message. Message type and content can be freely specified by the IMP client, however only certain message types are understood by message modules and only certain message contents can be processed by the integration system. The integration architecture will therefore have to adhere to the standard the IMP client specifies and adapt to possible future changes.

The "Attribute Change Message Module" consumes messages on the "Message Inbound" channel and filters all messages with types not related to attribute change. A message translator translates incoming message types to types the integration architecture can processes. This can be necessary, if for example the IMP client changes definitions of message types. A message router routes the messages to different channels depending on their type. In this case, two types of incoming messages can be processed on the "Attribute Change Request" channel and on the "Attribute Change Established" channel. To expand the list of message types the integration architecture can process, corresponding channel can be added.

Before publishing messages on the channels, a message translator translates the message content to a format, the integration architecture understands. This might be possible if in the future, the IMP client changes the format. A content filter removes unnecessary content from the message such as the message type, as modules will be able to infer it from the channel a message is published on.

The module is also able to process outbound messages originating from one of the modules. In this case, messages can arrive on the "Attribute Change Response" channel. A content filter removes unnecessary attributes attached to the message. In order to adapt to changes in the response format the IMP client understands, a message translator is attached. For the IMP client to understand the message, the implicit message type of the channel has to be added aThe module s an attribute. The resulting message is then published on the "Message Outbound" channel, where the messaging adapter instructs the connector to submit it.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 1/Technological Integration/10. Attribute Change Request Module.pdf}
\end{center}

To process incoming attribute change requests for profiles, a "Profile Attribute Change Request" module is included which consumes messages from the "Attribute Change Request" channel. To retrieve the user profile ID connected to the relationship ID, an incoming message is forwarded to the "Identity Mapping Request" channel. To eventually correlate the reply to the request, a content enricher adds a request ID to the message and stores the ID in a "Request ID Store".

Replies on the "Identity Mapping Response" channel which do not contain a request ID stored in the "Request ID Store" are filtered. The other messages are consumed by a message translator which, such as in previous modules, maps attributes shared as part of the attribute change request from the IMP data model to the OZG data model an publishes the message on the "Attribute Change Request" channel.

Similar to the "Onboarding Request Module", the decision whether to approve or reject an attribute change is specific to the service provider. Therefore, the SP is expected to include an "Attribute Change Processor" module, which based on the attribute change request, the relationship ID and the profile ID decides to approve or reject. The response is published to the "Attribute Change Response" channel and besides the response content contains the relationship ID.

The "Profile Attribute Change Request" module forwards the message to the "Attribute Change Response" channel, where the message module will further process it for delivery to the connector.

@@

If the user did not cancel the attribute change request before the OZG system accepted, the attribute change is established. The connector is notified trough a message, which eventually the "Profile Attribute Change Message" module described earlier will process and publish on the "Attribute Change Established" channel.

The "User Profile Attribute Sync" module consumes messages from the "Attribute Change Established" channel and similar to the "Profile Attribute Change Request" module, retrieves the profile ID corresponding to the relationship ID. Before publishing the response on the "User Profile Attribute Change" channel, the attributes are again translated from the IMP data model to the OZG data model. A channel adapter connected to the service facade consumes the message and updates the specified attributes for the specified user profile.

@@

In order for the user to receive messages sent to his user profile trough the IMP client, mail messages are processed by the integration architecture. Similar to the "Profile Attribute Change Message" module, a "Mail Message" module is included, which maps messages on the "Mail Outbound" channel to the "Message Outbound" channel.

In this module, incoming mails from the IMP client could also be processed, however this option is not included in the integration.

Trough a content filter, the module removes unimportant attributes from the message. A message translator is sued to translate the mail format of the user profile inbox to the format of the IMP client inbox. Eventually, a content enricher adds the implicit message type of the channel as attribute in order for the IMP client to understand it and publishes it on the "Message Outbound" channel.

@@

An messaging adapter attached to the service facade is notified each time, a user profile connected to an IMP identity receives a mail and publishes a message on the "Profile Mail Outbound" channel. The message contains the ID of the profile which received the message and the content of the mail. A "Mail" module is included which consumes the messages from the "Profile Mail Outbound" channel, retrieves the corresponding relationship ID, similar to previous modules, and publishes them on the "Mail Outbound" channel. The messages on the "Mail Outbound" channel are processed by the "Mail Message" module described earlier.

@@

If the user creates a user profile using his IMP identity, it is possible to replace authentication using a password with authentication trough the IMP client. It is also possible to use the IMP client for two factor authentication.

In order to send and receive messages related to authentication, similar to previous message modules, a "Authentication Message" module is included which maps incoming messages on the "Message Inbound" channel to the "Authentication Response" channel and outgoing messages from the "Authentication Request" channel to the "Message Outbound" channel.

@@

When the user visits the web page of the administration portal to apply for an administrative service, he will have to login. To utilize the IMP client for authentication, the web server can use a channel adapter to publish a authentication request concerning a user profile ID and a certain session ID. The adapter publishes a message on the "Authenticate" channel which contains the profile ID and a request content. Next to the session ID, the request content may also include information for presentation to the user like the current time or the IP address of the browser. Similar to previous modules, the relationship ID connected to the profile ID is retrieved and the response published on the "Authentication Request Message, where the "Authentication Message" module further processes the message and sends it to the connector.

Eventually, the IMP client sends a response as message, which the "Authentication Message" module publishes on the "Authentication Response" channel. As the message module already appropriately formatted the response content, the "Authentication" module can simply forward the message to the "Authenticated" channel. The channel adapter of the web server receives the message and based on the session ID contained in the response content can authenticate the browser session.

### 2021-02-26 sections/12-advanced_utilization.tex
added textual descriptions

The goal of this integration architecture is to make as much functionalities required for the basic OZG use case available through the IMP client. Now, the OZG user profiles are replaced with IMP identities and the integration architecture integrates with any system component necessary.

@@

>>>>

The goal of the advanced IMP utilization for OZG is to improve upon the solution presented in chapter 4 while allowing it to be modify and replace large portions of the existing system architecture.

@@

\subsection{Solution Evaluation}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Personal Information Existing Architecture.pdf}
\end{center}

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Overview.pdf}
\end{center}

\begin{itemize}

    \item Integration aufbauend auf erster oder ersetzend??

    \item Messaging architektur aus 1 genau so applizierbar in advanced integration

    \item im stil der overview der integrationen auch das connection diagram des OZG systems beschreiben. User Domain, Portal Domain, FIM Domain, Institution Domain, Data Exchange Domain

    \item basic use case umsetzen durch IMP trotz ablösen von 3 vorher existierenden domänen

    \item in diagrammen aufzeigen wo persönliche daten verarbeitet werden

    \item datenverabeitung vergleich zwischen diagrammen

    \item offen ob man andere domänen abschaltet (übergangszeit anlassen)

    \item benefit of module for each application type is, that the processing of applications with different legitimations is fully seperated and in the future new apllication types can be added without touching exisitng modules
\end{itemize}

### 2021-02-26 sections/13-imp_solution_integration.tex
added textual descriptions

\begin{itemize}
    \item The goal of this advanced integration is to take full advantage of IMP features

    \item The integration now focuses not only in the system architecture of the administration portal but also of the institutions

    \item A disadvantage of the previous integration solution is, that the administration portal maintains user profiles. This results in a duplication of user data management systems (IMP system and user profile system). In addition, trough the user profiles, the administration portal has access to personal information without the need for processing but routing it. This is a data protection issue.

    \item As institutions are the entities which eventually need to process personal information, personal information should only be shared with them.

    \item Using a IMP connector, institutions can establish relationships with users while the relationship represents the application for an administrative service.

    \item The institution does not maintain a identity management system in addition to the IMP system: An application is started being processed after the relationship is established and further communication regarding the application is done through the relationship. If the application is finished, the relationship is terminated, removing access to personal information for the institution.

    \item Institutions are capable of processing multiple administrative services. Each service has its own purpose, description and personal information required by the user. For each service, the institution processes, individual relationship templates can be created.

    \item In order for users to determine which institution is responsible for processing their request and for accessing the correct relationship template, the administration portal can be used as a "search-engine"

    \item The user searches for a administration service on the website of the administration portal and specifies the location he lives in. The administration portal determines the responsible institution and retrieves the correct relationship template from it.

    \item Based on the template, the user now interact only with the institution to apply for a service. The administration portal does not receive any further personal information.

    \item By requesting to change attributes of established relationships the institutions can process modifications of the request and decide if they accept or deny the request.

    \item As there is no standard for how the system of an institution operates, the integration can follow the integration of the administration portal by constructing a "form" from the shared personal information and enabling to deliver it in all kinds of formats through an adapter

    \item However, to further demonstrate the integration capabilities, the integration presents a possible integration for enabling application management through an E-Mail server on the institution side.

    \item Incoming applications can be sent as an E-Mail to employees assigned to a certain type of request. The relationship ID can be used as a reference ID in the title of the relationship or as a "spoofed" email sender. Further communication like attribute change requests can follow the same style and be aggregates by any email client to display all messages with the same reference ID.

    \item This method of applying for administrative services completely removes the need for administration portal and institution to maintain user profiles. It also enables users to share personal information only with entities which really need to process it. By enabling institution and user to directly interact, changes of the request content, status updates and exchange of mails can be done easily.

    \item Integration aufbauend auf erster oder ersetzend??

    \item Messaging architektur aus 1 genau so applizierbar in advanced integration

    \item im stil der overview der integrationen auch das connection diagram des OZG systems beschreiben. User Domain, Portal Domain, FIM Domain, Institution Domain, Data Exchange Domain

    \item basic use case umsetzen durch IMP trotz ablösen von 3 vorher existierenden domänen

    \item in diagrammen aufzeigen wo persönliche daten verarbeitet werden

    \item datenverabeitung vergleich zwischen diagrammen

    \item offen ob man andere domänen abschaltet (übergangszeit anlassen)

\end{itemize}

>>>>

The main issue of the IMP solution presented in chapter 4 is the utilization of user profiles and the resulting lack of data protection. The IMP solution described in this chapter puts the individual institutions in the center of the integration in order to eliminate the need for user profiles and the need for administration portals to process personal information.

Applications submitted to administration portals will eventually be submitted to responsible governmental institutions. Using IMP, relationships can be used to send applications directly to institutions without the need for an administration portal, form server or data exchange platform. Each institution has a predetermined set of administrative services it can process. For each administrative service, the institution can create relationship templates, containing a description of the service along with attributes required by the user:

\begin{itemize}
    \item Title: Apply for administrative service XYZ
    \item Attributes: Name, Surname, ... 
    \item Shared Attributes: Institution Name ...
    \item Reason: Apply for the administrative service XYZ ...
\end{itemize}

Based on these relationship templates, users and institutions can establish relationships. In contrast to the IMP solution of chapter 4, an established relationship does not result in the creation of a user profile. Instead, relationships represent a single application process and the attributes shared as part of the relationship are used by the institution to process the corresponding administrative service. After finishing the service, the relationship can be terminated, removing access to the shared attributes from the institution.

While processing the administrative service, institution and user can securely and directly exchange data such as mails trough the IMP system without the need of an administration portal or user profile being involved.

Providing an attribute change feature as described in chapter 4, can enable users to request modification of attributes of an active application. The institution can then decide whether to accept or reject the request.

For users to access the relationship templates, each institution can host its own web page which lists all administration services along with the corresponding QR code containing the template.

However, depending on for example the home address of the user, the institution responsible for processing an administrative service can change. Therefore the administration portals connected trough the online gateway can be used as a "search-engine" for institutions. On any administration portal a user can select an administrative service and specify his home address. Based on this information, the portal is able to determine the institution responsible for processing the request. However, instead of requiring the user to login to a profile, the portal can redirect him to the web page of the institution where the relationship templates are being displayed.

### 2021-02-26 sections/14-technological_integration.tex
added textual descriptions

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Integration Overview.pdf}
\end{center}

>>>>

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Overview.pdf}
\end{center}

To implement the solution described in the previous section, a connector is included in the existing system architecture of every institution. The same messaging system described in chapter 4 can be used to integrate the IMP solution described in the previous section. Many of the messaging modules can be reused with minor modifications. Similar to the messaging system in chapter 4, two system components are connected: A web server and a institution system.

As described in the previous section, for each administrative service, the institution is able to process, a relationship template is created and stored on a web page displayed by the web server. This can be done, as no personalized relationship templates will have to be created.

Therefore, the messaging system wont need modules for creating templates. However, modules for processing incoming relationship requests are required.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Request Module.pdf}
\end{center}

For each administrative service, separate types of relationship templates and therefore relationship requests exist. Each relationship request type is processed by its custom "Application Request" module and "Application Request Processing" module.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Relationship Module.pdf}
\end{center}

Application Relationship Modules consume messages from the "Relationship Established" and filter all requests not concerning the application type of the module. After that, attributes shared as part of the relationship are mapped from the IMP data model to the OZG data model. As the existing institution system expects applications to be delivered as a form created by the form server of the administration portal, a message translator is added which translates the shared attributes to a suitable format so that the institution system understands it. The message is then published on the "Process Application" channel where a messaging adapter connected to the institution system consumes the message and submits the included form to the institution system the same way as the data exchange platform would.

The institution system can use the unique relationship ID as reference ID for the application process and all further user interactions.

Similar to the "Profile Attribute Change Message" module a "Application Attribute Change Message" module can be included witch performs the same operations.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Attribute Change Request Module.pdf}
\end{center}

For processing attribute change requests, application attribute change request modules are included for each relationship type. They consume messages from the !Attribute Change Request" channel and filter messages which do not concern the application type of the module. After mapping the attributes from IMP data model to OZG data model, messages are published on the "Application Attribute Change Request" channel. A module of the service provider can, based on the provided relationship ID and shared attributes decide if the attributes of the active application can still be changed.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Attribute Sync Module.pdf}
\end{center}

In order to process the change of an attribute for an active application, application attribute sync modules are included for each relationship type. They first filter all messages not concerning the relationship type of the module, then translate all attributes from the IMP data model to the OZG data model and publish them on the "Application Attribute Change" channel.
A messaging adapter connected to the service facade consumes the messages and submits it to the institution system. In case the institution system has no way of processing an attribute change, a message translator can be included which constructs a form the messaging adapter submits as a new application with the same relationship ID.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Mail Message Module.pdf}
\end{center}

Using a bidirectional version of the "Mail Message" module, the messaging system can exchange mails from institution to IMP client and vice versa relating to a relationship ID.

\begin{center}
    \includegraphics[scale=0.6]{Diagrams/Integration Architecture 2/Application Mail Module.pdf}
\end{center}

For exchanging mails, application mail modules are included for each type of application.
